### 2018-10-15 Manuscript/Manuscript.tex
Updates from ShareLaTeX

To assess the statistical significance of the raw Pearson correlation coefficients,

I THINK HERE IN THE RESULTS IS WHERE THE MONTE CARLO APPROACH CAN BE ELUCIDATED. WE CAN SUCCINCTLY MAKE THE POINT THAT DIRECT CROSS-CORRELATION ISN'T APPROPRIATE WITHOUT SUCH NULL HYPOTHESIS TESTING. WE CAN PRESENT THAT THERE IS A WEAK POSITIVE CORRELATION WITH d2+b2 AND THEN DESCRIBE HOW THE RANDOM GENERATE GLACIAL INTERVAL APPROACH SHOWS THAT IT IS NOT SIGNIFICANT. THIS TEXT FROM THE FIG 4 CAPTION IS A START:
\textit{The only scenario for which there is a positive correlation coefficient related to ice extent and LIP area is that of a relatively slow decay rate (d2) and complete burial of LIPs associated with rifting (b2). This positive correlation is weak (\textit{r}=0.10) and is not significant as randomly timed glacial intervals correlate better than the record 28$\%$ of the time. With an associated p-value of 0.28, the null hypothesis that glacial intervals not related to LIP area in the tropics cannot be rejected.}

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.85\textwidth]{Manuscript/Figures/overlap_correlation_cropped.pdf}
	\caption{The overlap and correlation values for various LIP post-emplacement scenarios are shown with circles (d1 : LIP decay with half-life of 36~Myr; d2: LIP decay with half-life of~120 Myr; b1: 50\% burial of LIPs associated with rifting; b2: 100\% burial of LIPs associated with rifting). These values are compared to histograms that show the range of values that arise when comparing the LIP area record to glacial intervals that have been shifted randomly in time 100,000 times. The only scenario for which there is a positive correlation coefficient related to ice extent and LIP area is that of a relatively slow decay rate (d2) and complete burial of LIPs associated with rifting (b2). This positive correlation is weak (\textit{r}=0.10) and is not significant as randomly timed glacial intervals correlate better than the record 28\% of the time. With an associated p-value of 0.28, the null hypothesis that glacial intervals not related to LIP area in the tropics cannot be rejected.}
	\label{fig:LIP_correlation}
\end{center}
\end{figure}

>>>>

To assess the statistical significance of the raw Pearson correlation coefficients, we simulated the four glacial episodes (Fig. \ref{fig:LIP_area}E) occurring at random times through the past 520~Myr, and recomputed the correlation coefficient and \% overlap between the LIP area in the tropics and the randomly timed glacial intervals for each of these simulations. For all scenarios except for the `decay 2 + burial 2' scenario, more than half of the randomly timed glacial intervals correlate better with the LIP area in the tropics (Fig. \ref{fig:LIP_correlation}). For the `decay 2 + burial 2' scenario, 28\% of the randomly timed glacial intervals correlate better with the LIP area in the tropics. With an associated p-value of 0.28, the null hypothesis that glacial intervals do not correlate to LIP area in the tropics cannot be rejected.

@@

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.85\textwidth]{Manuscript/Figures/overlap_correlation_cropped.pdf}
	\caption{The overlap and correlation values for various LIP post-emplacement scenarios are shown with circles (d1 : LIP decay with half-life of 36~Myr; d2: LIP decay with half-life of~120 Myr; b1: 50\% burial of LIPs associated with rifting; b2: 100\% burial of LIPs associated with rifting). These values are compared to histograms that show the range of values that arise when comparing the LIP area record to glacial intervals that have been shifted randomly in time 100,000 times.}
	\label{fig:LIP_correlation}
\end{center}
\end{figure}
